Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-17 report/report.tex
Introduce the concept of path width

>>>>

In the 3D city model, each road will be represented by a polyline and a fixed \textbf{road width}. The width, or thickness, of a road at a certain point will be defined as the width of the perpendicular road cross section at that point, which is in its entirety usable by the intended types of traffic.
It is important to note that OSM does commonly not include a defition of the width of any road. An optional tag exists that lets users specify the average path width of a road, but this tag is rarely used in practise.
